--- 
title: "Solutions for 'Introdcution To The New Statistics'"
author: "Peter Baumgartner"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This website is a companion book for [Introduction to the New Statistics](https://www.routledgetextbooks.com/textbooks/9781138825529/) (abbreviated <i>itns</i>). It offers interactive exercises with solutions, and an R tutorial for the end-of-chapter exercises."
---

# Preface {-}

This interactive book is a companion book for [Introduction to the New Statistics](https://www.routledgetextbooks.com/textbooks/9781138825529/) (abbreviated <i>itns</i>). The two types of additional material it offers are:

+ interactive exercises with solutions, 
+ R tutorials for the end-of-chapter exercises.

## Interactive Exercises {-}

I have built the interactive exercises in this book with [H5P.org](https://h5p.org/). H5P stands for **H**TML**5** **P**ackage, a free and open-source content collaboration framework based on JavaScript. With H5P, it is easy for everyone to display, create, share, and reuse interactive HTML5 content through a standard browser. At the moment (February 2020), there are 45 different kinds of exercises ("content types" in H5P parlance). 

H5P content can be injected in any platform that supports embedded content (iframes). There exist already integrations for Learning Management Systems like [Canvas](https://www.instructure.com/canvas/), [Brightspace](https://www.d2l.com/products/), [Blackboard](https://www.blackboard.com/), [Moodle](https://moodle.org/) and other systems that support the standard for [**L**earning **T**ools **I**nteroperability](https://www.imsglobal.org/activity/learning-tools-interoperability) (See also: [How LTI works](https://www.imsglobal.org/basic-overview-how-lti-works)) In addition H5P has plugins developed for [WordPress](https://wordpress.org/plugins/h5p/), [Moodle](https://moodle.org/plugins/mod_hvp), [Drupal](https://www.drupal.org/project/h5p) and several other publishing systems. If you don't want to manage your own platform as a developer of interactive exercises you can also pay $57/month using [H5P.com](https://h5p.com/) **s**oftware **a**s **a** paid *s*ervice (SaaS).

I am using my German WordPress blog [Gedankensplitter](https://peter.baumgartner.name) with the required free H5P-plugin to develop interactive content presented in this book. I have tested these exercises at the backend site of my WordPress installation and --- if they work as intended --- I have published them here into the R-publishing system [bookdown](https://bookdown.org/yihui/bookdown/) via embedded code generated by the H5P WordPress plugin. As _bookdown_ is built on top of [R Markdown](https://rmarkdown.rstudio.com/), it is very suitable also to include the R tutorial.

Even if the technical handling process of developing interactive content with H5P is documented excellently and therefore relatively quickly done, there is another --- more educational --- difficulty. What kind of exercises are valuable to learn the content presented in **I**ntroduction to **T**he **N**ew **S**tatistics (abbreviated: itns)? 

Yes, there are some quizzes included in the book which one "only" has to transfer into H5P content. With the emphasis on "only," I want to address some difficulty resulting from converting static textual exercises into dynamic computer evaluated interactions. So, for instance, it is laborious to design the right solution for open-ended answers. But besides this more technical problem, there is also the more pressing issue to create valuable educational interactions with the tools provided by H5P.

Instead of using just traditional educational interactions on the web (most notably multiple-choice and fill-the-gap), I have experimented with a wide variety of different types of exercises. Furthermore, I have applied the concept of multiple representations by developing various tasks for the same content.

## R tutorial {-}

The second component of this companion book to _itns_ is a demonstration of how to carry out the statistical challenges presented in the end-of-chapter exercises using the programming language [R](https://www.r-project.org/), a free, open-source software environment for statistical computing and graphics. This part of the book is a tutorial. It applies R not only for the statistical analysis and visualization but also for other necessary practical tasks like data cleaning, data transformation, and data modeling. 

I assume some basic knowledge with the R language as I will not explain installation procedures and basic R commands. I am using [RStudio](https://rstudio.com/products/rstudio/download/), the prevalent free integrated development environment (IDE), and occasionally I mention RStudio specifics. But these hints are rare and not essential to understand and to replicate my suggested R procedures.

I will conclude the preface with a warning: I was intrigued by _itns_ as a new generation of a statistical textbook. Criticizing the standard null hypothesis significance testing (NHST) by using the estimation approach based on confidence intervals (CIs), meta-analysis, and integrating Open Science met my thinking and preferences.  But the truth is: I am neither a statistical expert nor an R wizard! My professional background is in instructional design and technology-enhanced learning (TEL). I am using the challenge to write this book as my particular vehicle to learn and practice statistical analysis and the R programming language. In this sense, I am just another learner applying the elaboration technique so splendid and convincing explained in "_Make it stick: The science of successful learning_" [@brown_make_2014].

<!-- TODO Preface: I need to explain the different formatting styles to support pedagogical goals of the book -->

<!-- TODO Preface: It may also be useful to explain how to use the different types of exercises -->

<!-- TODO Preface: Here, I need to include how to report errors or to suggest improvements and a section "acknowledgment". -->


## General Setup {-}

### Global Options {-}


```{r label = "global-options", highlight=TRUE}

### setting up working environment
### for details see: https://yihui.name/knitr/options/
knitr::opts_chunk$set(
        echo = T,
        message = T,
        error = T,
        warning = T,
        comment = '##',
        highlight = T,
        prompt = T,
        strip.white = T,
        tidy = T
        )

```

### Installing and loading R packages {-}


```{r installing-and-loading-R-packages}

### accompanying R package: https://github.com/gitrman/itns
if (!require("itns"))
        {remotes::install_github("gitrman/itns", 
                         build = TRUE, build_opts = c("--no-resave-data", "--no-manual"))
        library("itns")}


### https://www.tidyverse.org/
if (!require("tidyverse"))
        {install.packages("tidyverse", repos = 'http://cran.wu.ac.at/')
        library(tidyverse)}

### above command installed and loaded the core tidyverse packages:
# ggplot2: data visualisation
# tibble:  a modern take on data frames
# tidyr:   data tidying
# readr:   data import (csv, tsv, fwf)
# purrr:   functional R programming
# dplyr:   data (frame) manipulation
# stringr: string manipulation
# forcats: working with categorial varialbes


### to calculate mode:
if (!require("modeest"))
        {install.packages("modeest", repos = 'http://cran.wu.ac.at/')
        library(modeest)}

# I am going to use the `janitor` package for calculating table totals
if (!require("janitor"))
        {install.packages("janitor", repos = 'http://cran.wu.ac.at/')
        library(janitor)}

### install "checkr" to test code submissions in learnr (and potentially other) tutorials
### there is also a problem in line 639 in "vignettes/checkr.Rmd"
### I have changed version hoping that 0.6 is unsensible to the "older" CRAN version (0.4) and does not update
if (!require("checkr"))
        {remotes::install_github("petzi53/checkr2", 
                                 build = TRUE, build_opts = c("--no-resave-data", "--no-manual"))
        library(checkr)}

if (!require("itns"))
        {remotes::install_github("gitrman/itns", 
                         build = TRUE, build_opts = c("--no-resave-data", "--no-manual"))
        library("itns")}


```

### Theme adaption for the graphic display with `ggplot2` {-}

```{r generate-my-own-theme}

my_theme <- theme_light() +
        theme(plot.title = element_text(size = 10, face = "bold", hjust = 0.5))
        theme(plot.background = element_rect(color = NA, fill = NA)) +
        theme(plot.margin = margin(1, 0, 0, 0, unit = 'cm'))
```

